\LARGE \bf Simultaneous Hand-Eye and Robot-World Calibration by Solving the AX=YB Problem without Correspondence*

### 2015-11-17 submission/root.tex
Added another section for solving B^-1 Y^-1=X^-1 A^-1 problem

The hand-eye calibration problem can be modelled as $\textbf{AX = XB}$, where $A$ and $B$ are the homogeneous transformation matrices describing the relative motions of the end-effector and the  sensor respectively. As shown in Fig.~\ref{fig1} part (2), $A = A^{i}(A^{i+1})^{-1}$ and  $B = (B^{i})^{-1}B^{i+1}$. Given multiple pairs of $(A_i,B_i)$ with correspondence (note that $(A_i,B_i)$ are the relative transformations obtained from the raw data), many deterministic methods have been proposed to solve for $X$. To the best of the authors' knowledge, Shiu \cite{shiu1989calibration} and Tsai \cite{tsai1989new} are the first to solve the $AX = XB$ sensor calibration problem. The other methods include but are not limited to the quaternion, dual quaternion, screw theory, Lie group theory, motor algebra, convex optimization and gradient descent methods \cite{wang1992extrinsic,park1994robot,horaud1995hand,daniilidis1999hand,bayro2000motor,fassi2005hand,zhao2011hand,ackerman2014online}. All of the methods above assume a priori knowledge of the exact correspondence between $A_i$ and $B_i$. For data streams $\{A_i\}$ and $\{B_j\}$ that are asynchronous, several methods have been proposed in the litefit rature to solve for $X$ using data without a priori knowledge of the correspondence. These methods assume that there are some corresponding pairs of data in the streams of the $\{A_i\}$ and $\{B_j\}$; however,  the exact correspondence is unknown \cite{ackerman2013probabilistic, ackerman2014online ,ackerman2014information}.

@@

The rest of the paper is organized as follows. In Section
\ref{sect2}, a novel probabilistic method is presented to solve for eight candidates of $X$ and $Y$. In Section \ref{sect3}, an algorithm involving both correlation theorem and Euclidean group invariants is proposed to recover the correspondence between $\{A_i\}$ and $\{B_j\}$, which is used to select the optimal solution among the candidates. The simulation results obtained by taking noisy data without correspondence are illustrated in Section \ref{sect4}. Finally, conclusions are drawn based on the numerical results and possible future work is pointed out.

@@

\begin{equation}\label{equ7}
(\delta_{A_{i}}\ast \delta_{X})(H)=(\delta_{Y}\ast \delta_{B_{i}})(H)
\end{equation}
Defing the PDF %probability density function
of $\{A_i\}$ and $\{B_i\}$ as:
\begin{IEEEeqnarray}{l}\label{equ8}
f_{A}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta_{A_{i}}(H) \IEEEyessubnumber
\\*
f_{B}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta_{B_{i}}(H) \IEEEyessubnumber
\end{IEEEeqnarray}
then by using the distributivity of convolution, add $n$ instances of Eq.\textcolor{blue}{~}(\ref{equ7}), and substitute Eq.\textcolor{blue}{~}(\ref{equ8}) into the summation, and we will have:
\begin{equation}\label{equ9}
(f_{A_{i}}\ast \delta_{X})(H)=(\delta_{Y}\ast f_{B_{i}})(H)
%(f_{A_{i}}\ast \delta_{X})(g)=(\delta_{Y}\ast f_{B_{i}})(g)
\end{equation}

@@

\begin{IEEEeqnarray}{l}\label{equ11}
\int log(M^{-1}H))f(H)dH = \mathbb{O}  \IEEEyessubnumber
\\*
\Sigma = \int log^{\vee}(M^{-1}H)[log^{\vee}(M^{-1}H)]^{T}f(H)dH \IEEEyessubnumber
\end{IEEEeqnarray}
where the explicit expression of the matrix logarithm $log(H)$ along with its vectorized form $log^{\vee}(H)$ are given in \cite{chirikjian2011stochastic}.
If $f_A(H)$ is given as in Eq.~(\ref{equ8}), then the corresponding discrete version of the mean $M_A$ and covariance $\Sigma_A$ will be:

\begin{IEEEeqnarray}{l}\label{equ12}
\sum_{i=1}^{n}log(M_A^{-1}A_i)) = \mathbb{O} \IEEEyessubnumber
\\*
\Sigma = \sum_{i=1}^{n}log^{\vee}(M_A^{-1}A_i)[log^{\vee}(M_A^{-1}A_i)]^{T}. \IEEEyessubnumber
\end{IEEEeqnarray}

@@

The probabilistic method in this paper can recover the correspondence between shifted data streams, which is useful for other sensor calibration methods. In the $AX=YB$ problem, there have been many calibration methods developed for solving $X$ and $Y$ given data streams with correspondence. However, few of them considered the cases without correspondence. When data streams of ${A}$ and ${B}$ are shifted or asynchronous, most of these methods fail to give a valid solution. To further test the effectiveness of our method, we shift the data sequence of $\{A_i\}$ by $n=0,1,2,3,4,5$ with respect to the data sequence of $\{B_i\}$. We augment other $AX=YB$ solvers with our probabilistic approach. In Li's method \cite{li2010simultaneous}, $X$ and $Y$ are solved for at the same time while Shah \cite{shah2013solving} uses separable solutions to solve for $X$ and $Y$. In Fig.~\ref{fig5}, the correspondence between data streams is unknown and the errors on both rotations and translations are significant. After synchronizing the data streams by using the probabilistic method, Li and Shah's methods achieve the same level of performance as in the no-shift situation as shown in Fig.~\ref{fig6}.

\section{A Brief Case Study With Completely Scrambled Data}

@@

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,root}
%\begin{thebibliography}{1}
%
%
%\end{thebibliography}

>>>>

The hand-eye calibration problem can be modelled as $\textbf{AX = XB}$, where $A$ and $B$ are the homogeneous transformation matrices describing the relative motions of the end-effector and the  sensor respectively. As shown in Fig.~\ref{fig1} part (2), $A = A^{i}(A^{i+1})^{-1}$ and  $B = (B^{i})^{-1}B^{i+1}$. Given multiple pairs of $(A_i,B_i)$ with correspondence (note that $(A_i,B_i)$ are the relative transformations obtained from the raw data), many deterministic methods have been proposed to solve for $X$. To the best of the authors' knowledge, Shiu \cite{shiu1989calibration} and Tsai \cite{tsai1989new} are the first to solve the $AX = XB$ sensor calibration problem. The other methods include but are not limited to the quaternion, dual quaternion, screw theory, Lie group theory, motor algebra, convex optimization and gradient descent methods \cite{wang1992extrinsic,park1994robot,horaud1995hand,daniilidis1999hand,bayro2000motor,rovelo2008geometric, fassi2005hand,zhao2011hand,ackerman2014online}. All of the methods above assume a priori knowledge of the exact correspondence between $A_i$ and $B_i$. For data streams $\{A_i\}$ and $\{B_j\}$ that are asynchronous, several methods have been proposed in the litefit rature to solve for $X$ using data without a priori knowledge of the correspondence. These methods assume that there are some corresponding pairs of data in the streams of the $\{A_i\}$ and $\{B_j\}$; however,  the exact correspondence is unknown \cite{ackerman2013probabilistic, ackerman2014online ,ackerman2014information}.

@@

The rest of the paper is organized as follows. In Section
\ref{sect2}, a novel probabilistic method is presented to solve for eight candidates of $X$ and $Y$. In Section \ref{sect3}, an algorithm involving both correlation theorem and Euclidean group invariants is proposed to recover the correspondence between $\{A_i\}$ and $\{B_j\}$, which is used to select the optimal solution among the candidates. The simulation results obtained by taking noisy data without correspondence are illustrated in Section \ref{sect4}. In Section \ref{sect5}, we briefly discuss the case where one can obtain $\left( X, Y \right)$ without recovering the correspondence between the data sets.
Finally, conclusions are drawn based on the numerical results and possible future work is pointed out.

@@

\begin{equation}\label{equ7}
(\delta_{A_{i}}\ast \delta_{X})(H)=(\delta_{Y}\ast \delta_{B_{i}})(H)
\end{equation}
Defining the PDF %probability density function
of $\{A_i\}$ and $\{B_i\}$ as:
\begin{IEEEeqnarray}{l}\label{equ8}
f_{A}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta_{A_{i}}(H) \IEEEyessubnumber
\\*
f_{B}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta_{B_{i}}(H) \IEEEyessubnumber
\end{IEEEeqnarray}
then by using the distributivity of convolution, add $n$ instances of Eq.\textcolor{blue}{~}(\ref{equ7}), and substitute Eq.\textcolor{blue}{~}(\ref{equ8}) into the summation, and we will have:
\begin{equation}\label{equ9}
(f_{A_{i}}\ast \delta_{X})(H)=(\delta_{Y}\ast f_{B_{i}})(H)
%(f_{A_{i}}\ast \delta_{X})(g)=(\delta_{Y}\ast f_{B_{i}})(g)
\end{equation}

@@

\begin{IEEEeqnarray}{l}\label{equ11}
\int log(M^{-1}H)f(H)dH = \mathbb{O}  \IEEEyessubnumber
\\*
\Sigma = \int log^{\vee}(M^{-1}H)[log^{\vee}(M^{-1}H)]^{T}f(H)dH \IEEEyessubnumber
\end{IEEEeqnarray}
where the explicit expression of the matrix logarithm $log(H)$ along with its vectorized form $log^{\vee}(H)$ are given in \cite{chirikjian2011stochastic} as:

\begin{equation}
log(H) = \widehat{\bf h} 
=
\left(
\begin{array}{cccc}
   0 & -h_3 &  h_2 & h_4 \\ 
 h_3 &    0 & -h_1 & h_5 \\
-h_2 & -h_1 &    0 & h_6 \\
   0 &    0 &    0 &  0 
\end{array}
\right)
\end{equation}
where ${\bf h} = log^\vee(H) \in \mathbb{R}^{6 \times 1}$ and $\widehat{\bf h}$ is the corresponding Lie algebra element ($se(3)$) of $H$.

If $f_A(H)$ is given as in Eq.~(\ref{equ8}), then the corresponding discrete version of the mean $M_A$ and covariance $\Sigma_A$ will be:

\begin{IEEEeqnarray}{l}\label{equ12}
\sum_{i=1}^{n}log(M_A^{-1}A_i) = \mathbb{O} \IEEEyessubnumber
\\*
\Sigma = \sum_{i=1}^{n}log^{\vee}(M_A^{-1}A_i)[log^{\vee}(M_A^{-1}A_i)]^{T}. \IEEEyessubnumber
\end{IEEEeqnarray}

@@

The probabilistic method can recover the correspondence between shifted data streams, which is useful for other sensor calibration methods. In the $AX=YB$ problem, there have been many calibration methods developed for solving $X$ and $Y$ given data streams with correspondence. However, few of them considered the cases without correspondence. When data streams of ${A}$ and ${B}$ are shifted or asynchronous, most of these methods fail to give a valid solution. To further test the effectiveness of our method, we shift the data sequence of $\{A_i\}$ by $n=0,1,2,3,4,5$ with respect to the data sequence of $\{B_i\}$ such that $A_{k+n}$ ``matches'' $B_k$ where $k = 1, 2, \cdots, m-n$ and $i = 1,2, \cdots, m$. We augment other $AX=YB$ solvers with our probabilistic approach by recovering the correspondence between shift data sets. In Li's method \cite{li2010simultaneous}, $X$ and $Y$ are solved for at the same time, while Shah \cite{shah2013solving} solved for $X$ and $Y$ in a separate way. As shown in Fig.~\ref{fig5}, when dealing with the shifted data streams $\{A_{k+n}, B_k\}$, the errors on both rotations and translations are significant. After recovering the correspondence between data streams by using the probabilistic method, Li and Shah's methods achieve the same level of performance as shown in Fig.~\ref{fig6}.

\section{A Brief Case Study With Completely Scrambled Data}
\label{sect5}

In this section, we will briefly discuss the case where $\{A_i\}$ and $\{B_j\}$ are completely scrambled. Unlike the case of shifted data, it is extremely hard to recover the correspondence between two completely scrambled data sets $\{A_i\}$ and $\{B_j\}$. The correlation theorem can't be applied because there is no shift in the scrambled data sets. Euclidean group invariants are not practical either because given $\{A_i\}$ and $\{B_j\}$ both of which have the size of $m$, there are $m! = m \times m-1 \times \cdots 1$ combinations between the data sets, and it is extremely computationally intensive to test all the combinations. Without recovering the correspondence between the data sets, it is impossible to choose the optimal solution from the eight candidates of $\{X_k, Y_k\}$.

In the above approach, we used Eq.~(\ref{equ15b}) to calculate $X_k$ and Eq.~(\ref{equ15a}) to obtain the corresponding $Y_k$. However, we now show that one can calculate the eight candidates of $Y$ independently and employ Eq.~(\ref{equ15a}) as a constraint to filter out the optimal $\{X, Y\}$ pair.

Given the equation $AX=YB$, apply an inverse on both sides of the equation and we will have $B^{-1}Y^{-1} = X^{-1}A^{-1}$. Following the same derivations from Eq.~(\ref{equ5}) to Eq.~(\ref{equ15b}), and we have:
\begin{IEEEeqnarray}{l}
M_{B^{-1}} Y^{-1} = X^{-1} M_{A^{-1}} \IEEEyessubnumber\label{equ33a}
\\*
Ad(Y)\Sigma_{B^{-1}}Ad^{T}(Y) = \Sigma_{A^{-1}}. \IEEEyessubnumber\label{equ33b}
\end{IEEEeqnarray}
Similarly, Eq.~(\ref{equ33b}) can give eight candidates of $Y^{-1}$, or equivalently $Y$, Let $X_{k1}$ where $k1 = 1,2, \cdots, 8$ denote the $X$s obtained from Eq.(~\ref{equ15b}) and $Y_{k2}$ where $k2 = 1,2,\cdots, 8$ denote the $Y$s obtained from Eq.~(\ref{equ33b}), and we can use either Eq.~(\ref{equ15a}) or Eq.~(\ref{equ33a}) to get the optimal $\left( X_{k1}, Y_{k2} \right)$.

@@

\bibliographystyle{IEEEtran}
\bibliography{root}
%\bibliography{IEEEabrv,root}
%\begin{thebibliography}{1}
%
%
%\end{thebibliography}
